{\bf {\Large Title....}}

### 2016-07-08 ident_manu.Rnw
par_txt function to convert parameter chr strings to latex or R expression output

# L1, summaries
sensrng <- with(sens_ests_cat, which(L2 %in% range(L2))) %>% 
  sens_ests_cat[., ] %>% 
  mutate(error = sapply(error, scinot))

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temparature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).

>>>>

# L1 range
sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
  sens_ests_cat[., ] %>% 
  mutate(
    error = sapply(error, scinot),
    Parameter = par_txt(Parameter)
    )

# L1 range within categories
# sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
#   sens_ests_cat[., ] %>% 
#   mutate(
#     error = sapply(error, scinot),
#     Parameter = par_txt(Parameter)
#     )

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).  Within categories, sensitivity ranged from

### 2016-07-08 ident_manu.tex
par_txt function to convert parameter chr strings to latex or R expression output

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Jul 6 16:28:29 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temparature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $3.18\times 10^{-6}$ for Kcdom_1 (optics) to $328.35$ for Qc_1 (phytoplankton).

@@

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of phytoplankton parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter. Parameters less than the 75\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.\label{tab:phytosens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{coefficient for non-limiting nutrient}&&&\tabularnewline
~~\textit{aN\textsubscript{P1}}&$1$&$2.7$&$47.26$\tabularnewline
~~\textit{aN\textsubscript{P3}}&$1$&$0.66$&$3.16$\tabularnewline
\hline
{half-saturation constant for N}&&&\tabularnewline
~~\textit{Kn\textsubscript{P3}}&$5.93$&$1.15$&$9.22$\tabularnewline
~~\textit{Kn\textsubscript{P4}}&$1.13$&$0.62$&$2.5$\tabularnewline
\hline
{initial slope of the photosynthesis-irradiance relationship}&&&\tabularnewline
~~\textit{alpha\textsubscript{P4}}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
~~\textit{alpha\textsubscript{P3}}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
~~\textit{alpha\textsubscript{P5}}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
\hline
{minimum N cell-quota}&&&\tabularnewline
~~\textit{QminN\textsubscript{P3}}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
~~\textit{QminN\textsubscript{P4}}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
~~\textit{QminN\textsubscript{P1}}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
\hline
{mortality coefficient}&&&\tabularnewline
~~\textit{mA\textsubscript{P3}}&$0.03$&$2.98$&$14.34$\tabularnewline
~~\textit{mA\textsubscript{P4}}&$0.11$&$1.35$&$7.04$\tabularnewline
\hline
{N-uptake rate measured at umax}&&&\tabularnewline
~~\textit{vmaxN\textsubscript{P5}}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
~~\textit{vmaxN\textsubscript{P4}}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
~~\textit{vmaxN\textsubscript{P3}}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
~~\textit{vmaxN\textsubscript{P1}}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
\hline
{P-uptake rate measured at umax}&&&\tabularnewline
~~\textit{vmaxP\textsubscript{P3}}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
~~\textit{vmaxP\textsubscript{P1}}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
\hline
{phytoplankton basal respiration coefficient}&&&\tabularnewline
~~\textit{respb\textsubscript{P4}}&$0.02$&$3.1$&$26.48$\tabularnewline
~~\textit{respb\textsubscript{P3}}&$0.02$&$2.15$&$6.35$\tabularnewline
~~\textit{respb\textsubscript{P5}}&$0.02$&$0.81$&$8.61$\tabularnewline
\hline
{phytoplankton carbon/cell}&&&\tabularnewline
~~\textit{Qc\textsubscript{P1}}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
~~\textit{Qc\textsubscript{P3}}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
~~\textit{Qc\textsubscript{P2}}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
~~\textit{Qc\textsubscript{P4}}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
\hline
{phytoplankton growth respiration coefficient}&&&\tabularnewline
~~\textit{respg\textsubscript{P4}}&$0.1$&$0.98$&$7.37$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{Optimum temperature for growth(C)}&&&\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P4}}&$17$&$2.9$&$22.95$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{Z2}}&$26$&$0.18$&$2.59$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P5}}&$26$&$0.17$&$0.72$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P2}}&$22$&$0.16$&$0.82$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{Z1}}&$22$&$0.16$&$0.33$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P3}}&$17$&$0.14$&$0.78$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P1}}&$22$&$0.12$&$0.29$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of zooplankton parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:zoopsens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{assimilation efficiency as a fraction of ingestion}&&&\tabularnewline
~~\textit{Zeffic\textsubscript{P1}}&$0.4$&$0.23$&$0.55$\tabularnewline
~~\textit{Zeffic\textsubscript{P2}}&$0.4$&$0.21$&$0.75$\tabularnewline
\hline
{half saturation coefficient for grazing}&&&\tabularnewline
~~\textit{ZKa\textsubscript{P1}}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
~~\textit{ZKa\textsubscript{P2}}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
\hline
{maximum growth rate of zooplankton}&&&\tabularnewline
~~\textit{Zumax\textsubscript{P2}}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
~~\textit{Zumax\textsubscript{P1}}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
\hline
{proportion of grazed phytoplankton lost to sloppy feeding}&&&\tabularnewline
~~\textit{Zslop\textsubscript{P1}}&$0.25$&$0.12$&$0.33$\tabularnewline
\hline
{Zooplankton biomass-dependent respiration factor}&&&\tabularnewline
~~\textit{Zrespb\textsubscript{P1}}&$0.1$&$0.45$&$3.02$\tabularnewline
~~\textit{Zrespb\textsubscript{P2}}&$0.42$&$0.09$&$1.05$\tabularnewline
\hline
{zooplankton carbon/individual}&&&\tabularnewline
~~\textit{ZQc\textsubscript{P2}}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
~~\textit{ZQc\textsubscript{P1}}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
\hline
{Zooplankton growth-dependent respiration factor}&&&\tabularnewline
~~\textit{Zrespg\textsubscript{P1}}&$0.2$&$0.24$&$3.19$\tabularnewline
~~\textit{Zrespg\textsubscript{P2}}&$0.3$&$0.12$&$0.31$\tabularnewline
\hline
{Zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
~~\textit{Zm\textsubscript{P2}}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
~~\textit{Zm\textsubscript{P1}}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
\hline
{zooplankton nitrogen/individual}&&&\tabularnewline
~~\textit{ZQn\textsubscript{P1}}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
~~\textit{ZQn\textsubscript{P2}}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
\hline
{zooplankton phosphorus/individual}&&&\tabularnewline
~~\textit{ZQp\textsubscript{P2}}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
~~\textit{ZQp\textsubscript{P1}}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
\hline
\end{tabular}\end{center}}

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Thu Jul 7 15:16:18 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temparature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton).

@@

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of phytoplankton parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter. Parameters less than the 75\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.\label{tab:phytosens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{coefficient for non-limiting nutrient}&&&\tabularnewline
~~\textit{aN$_{p1}$}&$1$&$2.7$&$47.26$\tabularnewline
~~\textit{aN$_{p3}$}&$1$&$0.66$&$3.16$\tabularnewline
\hline
{half-saturation constant for n}&&&\tabularnewline
~~\textit{Kn$_{p3}$}&$5.93$&$1.15$&$9.22$\tabularnewline
~~\textit{Kn$_{p4}$}&$1.13$&$0.62$&$2.5$\tabularnewline
\hline
{initial slope of the photosynthesis-irradiance relationship}&&&\tabularnewline
~~\textit{alpha$_{p4}$}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
~~\textit{alpha$_{p3}$}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
~~\textit{alpha$_{p5}$}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
\hline
{minimum n cell-quota}&&&\tabularnewline
~~\textit{QminN$_{p3}$}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
~~\textit{QminN$_{p4}$}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
~~\textit{QminN$_{p1}$}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
\hline
{mortality coefficient}&&&\tabularnewline
~~\textit{mA$_{p3}$}&$0.03$&$2.98$&$14.34$\tabularnewline
~~\textit{mA$_{p4}$}&$0.11$&$1.35$&$7.04$\tabularnewline
\hline
{n-uptake rate measured at umax}&&&\tabularnewline
~~\textit{vmaxN$_{p5}$}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
~~\textit{vmaxN$_{p4}$}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
~~\textit{vmaxN$_{p3}$}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
~~\textit{vmaxN$_{p1}$}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
\hline
{p-uptake rate measured at umax}&&&\tabularnewline
~~\textit{vmaxP$_{p3}$}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
~~\textit{vmaxP$_{p1}$}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
\hline
{phytoplankton basal respiration coefficient}&&&\tabularnewline
~~\textit{respb$_{p4}$}&$0.02$&$3.1$&$26.48$\tabularnewline
~~\textit{respb$_{p3}$}&$0.02$&$2.15$&$6.35$\tabularnewline
~~\textit{respb$_{p5}$}&$0.02$&$0.81$&$8.61$\tabularnewline
\hline
{phytoplankton carbon/cell}&&&\tabularnewline
~~\textit{Qc$_{p1}$}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
~~\textit{Qc$_{p3}$}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
~~\textit{Qc$_{p2}$}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
~~\textit{Qc$_{p4}$}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
\hline
{phytoplankton growth respiration coefficient}&&&\tabularnewline
~~\textit{respg$_{p4}$}&$0.1$&$0.98$&$7.37$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{optimum temperature for growth(c)}&&&\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{p4}$}&$17$&$2.9$&$22.95$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{z2}$}&$26$&$0.18$&$2.59$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{p5}$}&$26$&$0.17$&$0.72$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{p2}$}&$22$&$0.16$&$0.82$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{z1}$}&$22$&$0.16$&$0.33$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{p3}$}&$17$&$0.14$&$0.78$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.12$&$0.29$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of zooplankton parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:zoopsens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{assimilation efficiency as a fraction of ingestion}&&&\tabularnewline
~~\textit{Zeffic$_{z1}$}&$0.4$&$0.23$&$0.55$\tabularnewline
~~\textit{Zeffic$_{z2}$}&$0.4$&$0.21$&$0.75$\tabularnewline
\hline
{half saturation coefficient for grazing}&&&\tabularnewline
~~\textit{ZKa$_{z1}$}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
~~\textit{ZKa$_{z2}$}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
\hline
{maximum growth rate of zooplankton}&&&\tabularnewline
~~\textit{Zumax$_{z2}$}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
~~\textit{Zumax$_{z1}$}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
\hline
{proportion of grazed phytoplankton lost to sloppy feeding}&&&\tabularnewline
~~\textit{Zslop$_{z1}$}&$0.25$&$0.12$&$0.33$\tabularnewline
\hline
{zooplankton biomass-dependent respiration factor}&&&\tabularnewline
~~\textit{Zrespb$_{z1}$}&$0.1$&$0.45$&$3.02$\tabularnewline
~~\textit{Zrespb$_{z2}$}&$0.42$&$0.09$&$1.05$\tabularnewline
\hline
{zooplankton carbon/individual}&&&\tabularnewline
~~\textit{ZQc$_{z2}$}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
~~\textit{ZQc$_{z1}$}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
\hline
{zooplankton growth-dependent respiration factor}&&&\tabularnewline
~~\textit{Zrespg$_{z1}$}&$0.2$&$0.24$&$3.19$\tabularnewline
~~\textit{Zrespg$_{z2}$}&$0.3$&$0.12$&$0.31$\tabularnewline
\hline
{zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
~~\textit{Zm$_{z2}$}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
~~\textit{Zm$_{z1}$}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
\hline
{zooplankton nitrogen/individual}&&&\tabularnewline
~~\textit{ZQn$_{z1}$}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
~~\textit{ZQn$_{z2}$}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
\hline
{zooplankton phosphorus/individual}&&&\tabularnewline
~~\textit{ZQp$_{z2}$}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
~~\textit{ZQp$_{z1}$}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
\hline
\end{tabular}\end{center}}
